Fusion Moves for Correlation Clustering

### 2014-11-07 paper/egpaper_for_review.tex

Agglomerative hierarchical clustering (HC) is widely used
in graph / image segmentation
\cite{arbelaez_2006}.
Hierarchical clustering is fast, and 
due to the agglomeration of edge weights, 
hierarchical clustering is robust against noise.
In agglomerative clustering, weights of
parallel edges are merged into single edges.
For image segmentation, the length
weighted mean is used to do this update.

We propose to use EHC find
solutions for correlation clustering.
In each step, the edge with the highest weight $w$ is
contracted (red edges in fig. ~\ref{fig:hc_alg}).
Doing so, parallel edges edges can occur.
Whenever there are multiple edges between 
a pair of nodes, these edges are merged into a single edge
by summing up their weights, since we 
minimize the sum of the cut edges.
The algorithm stops if the highest edge weight is
smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
contraction leads to worse energies.

Given the intrinsic greediness of hierarchical clustering, 
we do not expect very good solutions, but still a good starting 
point for move making algorithm as CGC \cite{beier_2014_cvpr}.
Therefore we propose to initialize  CGC with EBHC
and hope to speedup of CGC with this starting point.

Furthermore, we propose a algorithm to combine / fuse together
multiple EBHC results from perpetuated energies.
This algorithm, namely

\input{inputs/fig_hc_alg.tex} Correlation-Clustering-Fusion (CCF) Moves 
will be discussed in the following section.

>>>>

Agglomerative hierarchical clustering (HC) is widely used
in graph / image segmentation
\cite{arbelaez_2006}.

Hierarchical clustering is fast, and 
due to the agglomeration of edge weights, 
hierarchical clustering is robust against noise.
In agglomerative clustering, weights of
parallel edges are merged into single edges.
For image segmentation, the length
weighted mean is used to do this update.

We propose to use Energy Based Hierarchical Clustering (EHC) to find
solutions for correlation clustering.
In each step, the edge with the highest weight $w$ is
contracted (red edges in fig. ~\ref{fig:hc_alg}).
Doing so, parallel edges edges can occur.
To make EHC follow the energy, we propose 
the following update rule:
Whenever there are multiple edges between 
a pair of nodes, these edges are merged into a single edge
by summing up their weights, since we 
minimize the sum of the cut edges.
The algorithm stops if the highest edge weight is
smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
contraction leads to worse energies.

Given the intrinsic greediness of hierarchical clustering, 
and the fact that EHC does only local decisions, it is 
sensitive against salt and paper noise 
and we do not expect very good solutions.

But EHC is very fast, and can be used to initialize
CGC \cite{beier_2014_cvpr}. Excessive time in CGC
is spend in the \emph{cut phase} to solve the 
first 2 coloring on the complete graph.
As shown in ~\ref{sec:exp},
allowing CGC to start from the EHC solution
can improve performance drastically.

\input{inputs/fig_hc_alg.tex}
